### 2014-02-18 docs/seminar/evaluation.tex
accomplishing TODOs

As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kandell's. The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. TODO about significance test??.

>>>>

As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kendall's. The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. Regarding to P-Value of significance test shown in Table \ref{table:signtest}, a meaningful relation between GP2 and feedbacks can be considered. Top1 which has the worst values in the table shows a meaningless and near random correlation though.
